---
title: "Login module for ShinyApps"
subtitle: "shinymanager package"
institute: Zarathu Co., Ltd
author: "<br><br>Jinseob Kim; `r anicon::faa('github', animate='float', rtext='jinseob2kim')`"
date: "<br><br>2018-08-25, Updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
     lib_dir: libs
     css: ["shinobi", "ninjutsu" , "assets/ninpo.css"]
     nature:
      ratio: "4:3"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false 
---
exclude: true

<style type="text/css">
code.r{
  font-size: 16px;
}
pre {
  font-size: 16px !important;
}
</style>

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
library(knitr);library(DT);library(dplyr);library(data.table);library(rmarkdown);library(readr);library(purrr);library(tidyr)
```



---
class: bg-main1

# Executive Summary 

개인 PC에서 직접 **ShinyApps**를 이용할 수 있도록 
### Teach you how to learn R

--
.large[
- **ShinyApps**을 **[Rstudio Addins](https://rstudio.github.io/rstudioaddins/)**으로 만든 후, 이를 패키지로 만들어 **github**에 배포하였다.
]


---

class: middle bg-main1


## Now part of latest development version of `xaringan`
<br>
### `devtools::install_github('yihui/xaringan')`
<br>
### and add

```
output:
  xaringan::moon_reader:
    css: ["kunoichi", "ninjutsu"]
```


---
class: middle bg-main1

# How .yellow[should] you use R?


---
class: bg-main1

# Making your R work .yellow[organized] and .yellow[portable]


---

class: bg-main1 split-30 hide-slide-number

.column.bg-main3[
]
.column.slide-in-right[
.sliderbox.bg-main2.vmiddle[
.font5[Split Cells]
]]



---

class: split-two white

.column.bg-main1[.content[
# A .yellow[kunoichi] can use .yellow[ninjutsu] to .green[split columns] easily.
<br>
## Define your classes as*
```{}
class: split-two white
```

## Columns are added easily by 
```{r, eval=F}
{{.column.bg-main1[.content[}}
  content of first column
]]
{{.column.bg-main2[.content[}}
  content of second column
]]
```
]]
.column.bg-main2[.content.vmiddle.center[
# See the R-markdown source file for this slide [here](https://github.com/emitanaka/ninja-theme).
<br><br>
# * class white changes all the font to white
]]